\cvsection{PROFESSIONAL EXPERIENCE}

\begin{cventries}

    \cventry
        {Software Engineer}
        {Cloudly Infotech Ltd.}
        {Hybrid - Dhaka, Bangladesh}
        {January 2025 - Present}
        {
            \begin{cvitems}
                \item {Developed frontend architecture for an ML/AI-powered telecom network optimization platform, integrating RESTful APIs for user authentication, tenant management, resource management, and AWS S3 bucket operations to enable secure multi-tenant data access and storage.}
                \item {Built interactive dashboards with real-time optimization graph visualizations using modern frontend frameworks, presenting complex network performance metrics.}
                \item {Implemented comprehensive API integration layer connecting frontend application with backend workflow services, enabling seamless data flow between user interactions and ML inference pipelines for network optimization insights.}
                \item {Engineered frontend infrastructure using Docker containerization, implementing build optimization and deployment strategies that ensured consistent development and production environments across AWS cloud infrastructure.}
                \item {Developed reusable component libraries and state management solutions for handling complex data visualization requirements, improving development velocity and maintaining consistent UI/UX patterns across the platform.}
                \item {Integrated AWS S3 SDK for client-side file upload workflows with progress tracking and error handling, optimizing large dataset transfers between frontend application and cloud storage infrastructure.}
            \end{cvitems}
        }

    \cventry
        {Contractual \& Part time}
        {Freelance Web Engineer}
        {Remote - Dhaka, Bangladesh}
        {January 2015 - Present}
        {
            \begin{cvitems}
                \item {Provided full-stack website development solutions using WordPress, ReactJS, NodeJS, and other modern web application technologies.}
                \item {Built websites and web applications using HTML, CSS, JavaScript, JS Frameworks etc.}
                \item {Utilized modern web technologies to develop custom solutions for diverse industries.}
                \item {Planned and engineered RESTful web services to manipulate dynamic datasets.}
            \end{cvitems}
        }

    \cventry
        {Senior Front-End Engineer}
        {Curotec}
        {Remote - Pennsylvania, USA}
        {June 2022 - May 2023}
        {
            \begin{cvitems}
                \item {Developed and delivered 5+ industry-standard web applications using ReactJS, NextJS, Bootstrap, and Laravel, enhancing client satisfaction and achieving a 25\% increase in user engagement.}
                \item {Ensured seamless user experiences with 100\% cross-browser compatibility and implementing performance optimizations, resulting in a 20\% increase in performance scores.}
                \item {Strengthened communication skills through regular interactions with others.}
                \item {Resolved complex issues, enhanced operational efficiency by 30\%, and consistently delivered exceptional service, contributing to a 25\% increase in customer satisfaction.}
            \end{cvitems}
        }

    \cventry
        {Front-End Engineer}
        {Reformed Tech}
        {Dhaka, Bangladesh}
        {June 2021 - July 2022}
        {
            \begin{cvitems}
                \item {Designed and implemented robust Content Management Systems, enhancing client interface efficiency by 40\% and reducing content update times by 30\%.}
                \item {Took concepts and produced design mock-ups and prototypes to strengthen designs, enhance user experiences, and improve site interactions.}
                \item {Worked closely with UX / UI designers to implement visually appealing interfaces that met client requirements.}
                \item {Performed security maintenance and patching on the website interface, ensuring 99.9\% uptime and safeguarding post-launch viability.}
                \item {Conducted unit testing and resolved issues in web applications, achieving a 95\% bug resolution rate and enhancing overall application stability.}
            \end{cvitems}
        }

    \cventry
        {Front-End Engineer}
        {XpeedStudio}
        {Dhaka, Bangladesh}
        {May 2020 - May 2021}
        {
            \begin{cvitems}
                \item {Contributed to creating powerful WordPress plugins to aid users build websites using Elementor.}
                \item {Created web-based admin dashboards to manage plugin administrative tasks.}
                \item {Created several WordPress themes published on community markets.}
            \end{cvitems}
        }

\end{cventries}

\cvsection{INTERNSHIPS}

\begin{cventries}

    \cventry
        {Intern Software Engineer}
        {Bangladesh Venture Capital Ltd.}
        {Dhaka, Bangladesh}
        {January 2018 - March 2019}
        {
            \begin{cvitems}
                \item {Developed a virtual currency wallet application for in-campus facility transactions within my university.}
                \item {Gained hands-on experience while collaborating with a team to deliver a secure and user-friendly application.}
                \item {Prepared project presentations and reports to assist senior staff.}
                \item {Participated in workshops and presentations related to projects to gain knowledge.}
            \end{cvitems}
        }

\end{cventries}
